Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-18 manuscript/manuscript.tex
methods updated
added bambus2 result

\begin{figure*}[htbp]
\centering
\includegraphics[width=\textwidth]{es_mix_200kb_k21.png}
\caption{Assembly graph of a simulated community consisting of 200 Kbp subsets of \textit{Escherichia coli} str. K-12 MG1655 and \textit{Staphylococcus aureus}.  Nodes are colored and sized based on their relative betweenness centrality. The highlighted nodes are inter-genomic repeats whose deletion would separate the graph. Note that the betweenness centrality measure correctly identifies these nodes.}
\label{fig:sampled_nodes}
\end{figure*}

@@

\subsection*{Results On Real Metagenomic Datasets}
We evaluated the runtime of Bambus2's repeat detection module on metagonic stool sample. It

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[width=0.60\textwidth]{es_mix_200kb_k21.png}
\caption{Assembly graph of a simulated community consisting of 200 Kbp subsets of \textit{Escherichia coli} str. K-12 MG1655 and \textit{Staphylococcus aureus}.  Nodes are colored and sized based on their relative betweenness centrality. The highlighted nodes are inter-genomic repeats whose deletion would separate the graph. Note that the betweenness centrality measure correctly identifies these nodes.}
\label{fig:sampled_nodes}
\end{figure*}

@@

\subsection*{Results On Real Metagenomic Datasets}
We evaluated the performance of approximate betweenness centrality algorithms on metagenomic stool sample. We compared the performance of these algorithms with Bambus2 repeat detection module. Bambus2 repeat detection module took over 50 hours to find repeats in this graph. The algorithm based on sampling shortest paths took 312.69 seconds for $\epsilon = 0.1$ to find out repeats. The algorithm based on sampling nodes took 469 seconds for the sample of 1000 nodes and around 5000 seconds(1.3 hours) for the sample of 10000 nodes. From these results it can be concluded that we can use approximation algorithms for repeat finding and get significant speedups.
